Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features

### 2021-04-28 publication/manuscript.Rmd
add text

```{r, rank-res, out.height=".55\\textwidth", fig.cap='(ref:rank-res)', out.width="\\textwidth"}
plotdt = rbindlist(lapply(names(cons_list), function(x) {
  r = relation_class_ids(cons_list[[x]][[1]])
  data.frame(method = names(r), rank = r, algorithm = x)
}))
set(plotdt, which(plotdt$method == "remove" & plotdt$algorithm == "RF"), "rank", 11)
plotdt = plotdt[-which(plotdt$method == "none"),]
p = ggplot(plotdt, aes(x = rank, y = algorithm, fill = method)) +
 geom_tile(size = .5, width =.93, height =.93, color = "black")
p = p +
  theme_minimal() +
  theme(
    axis.title.x = element_blank(),
    legend.spacing.x = unit(0.1, "cm"),
    legend.key.size = unit(.9, "cm")
  ) +
  theme(axis.title.y=element_blank()) +
  theme(legend.background = element_blank()) +
  theme(legend.key = element_blank()) +
  theme(legend.title = element_blank()) +
  scale_fill_manual(values = box_colors) +
  theme(panel.grid.minor.y = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.grid.minor.x = element_blank()) +
  theme(panel.grid.major.x = element_blank()) +
  scale_x_continuous(breaks = c(1:11), expand = c(0, 0))
p
```
<!--

>>>>

```{r, rank-res, out.height=".55\\textwidth", fig.cap='(ref:rank-res)', out.width="\\textwidth"}
plotdt = rbindlist(lapply(names(cons_list), function(x) {
  r = relation_class_ids(cons_list[[x]][[1]])
  data.frame(method = names(r), rank = r, algorithm = x)
}))
set(plotdt, which(plotdt$method == "remove" & plotdt$algorithm == "RF"), "rank", 11)
plotdt = plotdt[-which(plotdt$method == "none"),]

swit = Vectorize(function(x) {
  switch(x,
  "frequency" = "frq",
  "one-hot" = "oh",
  "remove" = "rm",
  "integer" = "int",
  "dummy" = "dumm",
  "leaf" = "leaf",
  "impact" = "imp",
  "glmm-10CV" = "CV10",
  "glmm-5CV" = "CV5",
  "glmm-noCV" = "noCV",
  "hash" = "hash"
)})
plotdt$lab = unlist(swit(plotdt$method))

p = ggplot(plotdt, aes(x = rank, y = algorithm, fill = method)) +
 geom_tile(size = .5, width =.93, height =.93, color = "black") +
 geom_text(aes(x=rank, y = algorithm, label=lab), size = 3)

p = p +
  theme_minimal() +
  theme(
    axis.title.x = element_blank(),
    legend.spacing.x = unit(0.1, "cm"),
    legend.key.size = unit(.9, "cm")
  ) +
  theme(axis.title.y=element_blank()) +
  theme(legend.background = element_blank()) +
  theme(legend.key = element_blank()) +
  theme(legend.title = element_blank()) +
  scale_fill_manual(values = box_colors) +
  theme(panel.grid.minor.y = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.grid.minor.x = element_blank()) +
  theme(panel.grid.major.x = element_blank()) +
  scale_x_continuous(breaks = c(1:11), expand = c(0, 0))
p
```
<!--
